Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-11-19 main.Rmd
before structure change where noralisation is one section

mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds")
data_long = mmpd_raw %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels")
The null hypothesis is that the two cyclic granularities do not differ on the outcome (i.e., that the outcome is observed independently of treatment assignment). When we permute the outcome values during the test, we therefore see all of the possible alternative treatment assignments we could have had and where the mean-difference in our observed data falls relative to all of the differences we could have seen if the outcome was independent of treatment assignment. While a permutation test requires that we see all possible permutations of the data (which can become quite large), we can easily conduct “approximate permutation tests” by simply conducting a vary large number of resamples. That process should, in expectation, approximate the permutation distribution.

@@

```{r hist_plot, fig.cap="density mmpd raw"}
 hist_plot = mmpd_raw %>% 
      ggplot() +
      geom_density(aes(x = raw_mmpd), fill = "blue") +
      facet_grid(nx~nfacet)
hist_plot
```

>>>>

The null hypothesis is that the two cyclic granularities do not differ on the outcome (i.e., that the outcome is observed independently of treatment assignment). When we permute the outcome values during the test, we therefore see all of the possible alternative treatment assignments we could have had and where the mean-difference in our observed data falls relative to all of the differences we could have seen if the outcome was independent of treatment assignment. While a permutation test requires that we see all possible permutations of the data (which can become quite large), we can easily conduct “approximate permutation tests” by simply conducting a vary large number of resamples. That process should, in expectation, approximate the permutation distribution.

@@

```{r hist-plot, fig.cap = "density mmpd raw"}
mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds") 
mmpd_xmore = read_rds("../hakear-drake/data/data_all213045x.rds") 
mmpd_fmore = read_rds("../hakear-drake/data/data_all_213045f_allx.rds")

data_all = bind_rows(mmpd_raw, mmpd_xmore, mmpd_fmore)

data_long = data_all %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels")

g1 <- data_all %>% 
  filter(!(nx %in% c(3, 4))) %>% 
  ggplot() +
  ggridges::geom_density_ridges(aes(x = raw_mmpd, 
                                    y = as.factor(nfacet))) +
  facet_wrap(~nx, nrow = 2)

g2 <- data_all %>% 
  filter(nfacet<=14, nfacet!=3) %>% 
  ggplot() +
  geom_boxplot(aes(y = raw_mmpd, 
                                    x = as.factor(nx))) +
  facet_wrap(~nfacet) + coord_flip()

#  hist_plot = data_all %>% 
#       ggplot() +
#       geom_density(aes(x = raw_mmpd), fill = "blue") +
#       facet_grid(nx~nfacet)
# hist_plot
library(patchwork)
g1/g2
```
